---
title: "Project 2"
author: "Peter, Lukas & Rasmus"
date: "15/1/2020"
output:
  word_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# set seed
set.seed(-2000)

# packages
library(ggplot2)
library(magrittr)
```



# Data

```{r echo=FALSE}
data_fos <- get(load("fosfor_data.Rdata")) %>% 
  data.frame() %>% 
  dplyr::mutate(location = as.factor(location))
data_fos

```

## Summaries

```{r}
cat("Structure")
str(data_fos)
cat("Summary")
summary(data_fos)
cat("Data")
data_fos

# nas <- which(is.na(data_fos$yield)) 
# data_fos[unique(c(nas, nas+1, nas-1)), ]

#xtable::xtable(summary(data_fos, maxsum = 9)) #converts to latex

      
```

## Handle NA's

Uses KNN imputation and looks at the k nearest neighbors, the missing value is then replaced with the average of the values for the nearest neighbors

```{r}
data_fos <- DMwR::knnImputation(data_fos,k=2, meth = "Median")
```

## grouped data set

groups the data, so that there is only one yield for each combination of location, DGT and olsenP, which is the mean. THis is done as these three factors are strongly dependent of each other.

```{r}
data_grouped <- data_fos %>% dplyr::group_by(location, DGT, olsenP) %>% dplyr::summarise_each(mean)
data_grouped

ggplot(tidyr::gather(data_grouped, "key", "value", -c(location, yield)), aes(value, yield, col = location)) +
  geom_point() +
  facet_wrap("key", scales = "free")
```


## Plots

Comparison plot

```{r}
GGally::ggpairs(data_fos, columns = c("DGT", "olsenP", "yield"), title = "Data summary")
ggsave("data_plot.jpg")
```

Boxplots

```{r}
#par(mfrow = c(3,1))
boxplot(yield ~location, data = data_fos)
boxplot(DGT ~ location, data = data_fos)
boxplot(olsenP ~ location, data = data_fos)

data_fos %>% 
  tidyr::gather("key", "value", -location) %>%
  dplyr::filter(key == "yield") %>% 
  dplyr::rename(yield = value) %>% 
  ggplot(aes(x = location, y = yield)) + 
    geom_boxplot(fill = 'green') 
ggsave("boxplot_yield_location.jpg")


```

Scatter plots

```{r}
par(mfrow = c(1,2))
plot(data = data_fos , yield ~ olsenP)
plot(data = data_fos , yield ~ DGT)
```

# OlsenP vs. DGT

## ANOVA

```{r}
lm1 <- lm(data = data_fos, formula = yield ~ DGT)
summary(lm1)


lm2 <- lm(data = data_fos, formula = yield ~ olsenP)
summary(lm2)

# lm3 <- lm(data = data_fos, formula = yield ~ location)
# anova(lm3)
# summary(lm3)


phos.model.DGT <- nls(yield ~ alfa * DGT/(beta + DGT) , data = data_fos,
start = list(alfa = 90 , beta = 1))

phos.model.olsenP <- nls(yield ~ alfa * olsenP/(beta + olsenP) , data = data_fos,
start = list(alfa = 90 , beta = 1))

phos.model.DGT_mean <- nls(yield ~ alfa * DGT/(beta + DGT) , data = data_grouped,
start = list(alfa = 90 , beta = 1))


phos.model.olsenP_mean <- nls(yield ~ alfa * olsenP/(beta + olsenP) , data = data_grouped,
start = list(alfa = 90 , beta = 1))

phos.model.DGT_lm <- lm(yield ~ DGT , data = data_fos)

phos.model.olsenP_lm <- lm(yield ~ olsenP, data = data_fos)

summary(phos.model.DGT)
summary(phos.model.olsenP)


# lm_august <- nls(yield ~ a * olsenP/(b+olsenP), data = data_fos, start = list(b = max(data_fos$yield)/2, a = max(data_fos$yield)))
# anova(lm_august)
# summary(lm_august)
# coef(lm_august)
# lm_august
# phos.model.olsenP

```

### Plots of model coefficients

```{r}
par(mfrow=(c(3,2)))
alfa_DGT <- coef(phos.model.DGT)[1]
beta_DGT <- coef(phos.model.DGT)[2]
alfa_olsenP <- coef(phos.model.olsenP)[1]
beta_olsenP <- coef(phos.model.olsenP)[2]
alfa3 <- coef(phos.model.DGT_mean)[1]
beta3 <- coef(phos.model.DGT_mean)[2]
alfa4 <- coef(phos.model.olsenP_mean)[1]
beta4 <- coef(phos.model.olsenP_mean)[2]


# plot(data = data_fos , yield ~ DGT)
# lines(x<-c(1:200),(alfa1 * x )/(beta1 + x),col='red')
# plot(data = data_fos , yield ~ olsenP)
# lines(x<-c(1:200),(alfa2 * x )/(beta2 + x),col='red')
# plot(data = data_grouped , yield ~ DGT)
# lines(x<-c(1:200),(alfa3 * x )/(beta3 + x),col='red')
# plot(data = data_grouped , yield ~ olsenP)
# lines(x<-c(1:200),(alfa4 * x )/(beta4 + x),col='red')
# 
# 
# plot(data = data_fos , yield ~ DGT)
# abline(coef(phos.model.DGT_lm))
# plot(data = data_fos , yield ~ olsenP)
# abline(coef(phos.model.olsenP_lm))

beta_olsenP
# ggplot
rep_p <- nrow(data_fos)
data_plot <- data_fos %>% 
  tidyr::gather("method", "value", DGT, olsenP) %>% 
  dplyr::mutate(method = as.factor(method),
                slope = c(rep(coef(phos.model.DGT_lm)[2], rep_p), 
                          rep(coef(phos.model.olsenP_lm)[2], rep_p)),
                intercept = c(rep(coef(phos.model.DGT_lm)[1], rep_p), 
                              rep(coef(phos.model.olsenP_lm)[1], rep_p)),
                alfas = c(rep(alfa_DGT, rep_p), rep(alfa_olsenP, rep_p)),
                betas = c(rep(beta_DGT, rep_p), rep(beta_olsenP, rep_p)))

levels(data_plot$method) <- c("DGT [µg/L]", "olsenP [mg/100 g]")

ggplot(data_plot, aes(x = value, y = yield)) +
  geom_point() +
  #geom_abline(data = data_plot, mapping = aes(slope = slope, intercept = intercept, col = "Linear")) +
  stat_smooth(method = 'nls', formula = 'y ~ alfa * x/(beta + x)',
               method.args = list(start=list(alfa = 90 , beta = 1)), se=F, data = data_plot, mapping = aes(col = "Michaelis-Menten")) +
  facet_wrap(~method, scales = "free") +
  xlab("Bioavailable phosphorous") +
  ylab("Yield [hkg/ha.]") +
  theme(legend.title = element_blank()) +
  theme(legend.position = "bottom")

ggsave("model_comparison_no_reg.png")


```

### Bootstrapping - Konfidensintervaller for bestemmelse af parametrene
Både parametrisk og ikke parametrisk
```{r}
N <- 1000
set.seed(2020)

residual_SD_DGT <- sd(summary(phos.model.DGT_mean)$residuals)
residual_SD_olsenP <- sd(summary(phos.model.olsenP_mean)$residuals)

BS_coef <- c()

data_NPBS <- data_fos
data_PBS <- data_grouped
BS_list_Yield <- split(data_NPBS$yield, data_NPBS$location)
BS_list_DGT <- split(data_NPBS$DGT, data_NPBS$location)
BS_list_olsenP <- split(data_NPBS$olsenP, data_NPBS$location)
pred_DGT <- predict(phos.model.DGT_mean)
pred_olsenP <- predict(phos.model.olsenP_mean)

for (i in 1:N){
  if (i %% 100 == 0){
    print(i)
  }
  BS_DGT_parametric <- pred_DGT + rnorm(9, 0, residual_SD_DGT)
  BS_olsenP_parametric <- pred_olsenP + rnorm(9, 0, residual_SD_olsenP)
  
  s <- sample(9, replace = T)
  data_NPBS$yield_nonP <- unlist(BS_list_Yield[s])
  data_NPBS$DGT_nonP <- unlist(BS_list_DGT[s])
  data_NPBS$olsenP_nonP <- unlist(BS_list_olsenP[s])
  
  
  data_PBS$yield_P_DGT <- BS_DGT_parametric
  data_PBS$yield_P_olsenP <- BS_olsenP_parametric

  
  
  phos.model.DGT_P_BS <- nls(yield_P_DGT~ alfa * DGT/(beta + DGT), data = data_PBS, start = list(alfa = 90 , beta = 1), nls.control(warnOnly = T))
  
  phos.model.olsenP_P_BS <- nls(yield_P_olsenP ~ alfa * olsenP/(beta + olsenP), data = data_PBS, start = list(alfa = 90 , beta = 1), nls.control(warnOnly = T))
  
    phos.model.DGT_NP_BS <- nls(yield_nonP ~ alfa * DGT_nonP/(beta + DGT_nonP), data = data_NPBS, start = list(alfa = 90 , beta = 1), nls.control(warnOnly = T))
  
  phos.model.olsenP_NP_BS <- nls(yield_nonP ~ alfa * olsenP_nonP/(beta + olsenP_nonP), data = data_NPBS, start = list(alfa = 90 , beta = 1), nls.control(warnOnly = T))
  
  
  BS_coef <- rbind(BS_coef, c(coef(phos.model.DGT_P_BS),coef(phos.model.olsenP_P_BS), coef(phos.model.DGT_NP_BS), coef(phos.model.olsenP_NP_BS)))
  
  
}
BS_coef <- as.data.frame(BS_coef)
names(BS_coef) <- c("alfa_DGT","beta_DGT","alfa_olsenP","beta_olsenP","alfa_DGT2","beta_DGT2","alfa_olsenP2","beta_olsenP2")
par(mfrow=c(2,2))
hist(BS_coef$alfa_DGT)
abline(v = alfa_DGT, col = 3)
hist(BS_coef$beta_DGT)
abline(v = beta_DGT, col = 3)
hist(BS_coef$alfa_olsenP)
abline(v = alfa_olsenP, col = 3)
hist(BS_coef$beta_olsenP)
abline(v = beta_olsenP, col = 3)

CIs <- data.frame(cbind(rbind(quantile(BS_coef$alfa_DGT, c(0.025, 0.975)), 
quantile(BS_coef$beta_DGT, c(0.025, 0.975)),
quantile(BS_coef$alfa_olsenP, c(0.025, 0.975)),
quantile(BS_coef$beta_olsenP, c(0.025, 0.975))), 
rbind(quantile(BS_coef$alfa_DGT2, c(0.025, 0.975)), 
quantile(BS_coef$beta_DGT2, c(0.025, 0.975)),
quantile(BS_coef$alfa_olsenP2, c(0.025, 0.975)),
quantile(BS_coef$beta_olsenP2, c(0.025, 0.975)))),
row.names = c("alfa_DGT","beta_DGT", "alfa_olsenP", "beta_olsenP"))
names(CIs) <- c("Paramtric 2.5 %", "Parametric 97.5 %","Normal 2.5 %", "Normal 97.5 %")
CIs

```




#  Predicting Yield
## "Leave 4 out" - cross validation
Bestemmere MSE for begge modeller ved cross validation, hvor i hvert fold udelukkes en location

```{r}
set.seed(-1825)
data_CV <- data_fos
level <- levels(data_CV$location)
N <- length(level)

s <- sample(N)
K_fold <- N


accuracy <- c()
random_index <- split(sample(c(1:N),N), c(1:K_fold))
loss <- c()

for (i in c(1:K_fold)){


  train_set <- subset(data_CV, location != level[i])
  test_set <- subset(data_CV, location == level[i])
  model_cv_DGT <- phos.model.DGT_perm <- nls(yield ~ alfa * DGT/(beta + DGT) , data = train_set,
                        start = list(alfa = 90 , beta = 1),na.action = na.exclude)
  
  model_cv_olsenP <- phos.model.DGT_perm <- nls(yield ~ alfa * olsenP/(beta + olsenP) , data = train_set,
                        start = list(alfa = 90 , beta = 1), na.action = na.exclude)
  
  lm_model_DGT <- lm(data = data_fos, formula = yield ~ DGT)
  lm_model_olsenP <- lm(data = data_fos, formula = yield ~ olsenP)
  
  
  pred_DGT <- predict(model_cv_DGT, test_set)
  pred_olsenP <- predict(model_cv_olsenP, test_set)

  pred_lmDGT <- predict(lm_model_DGT, test_set)
  pred_lmolsenP <- predict(lm_model_olsenP, test_set)

  
  error_DGT <- (test_set$yield - pred_DGT)^2
  error_olsenP <- (test_set$yield - pred_olsenP)^2
  
  error_lmDGT <- (test_set$yield - pred_lmDGT)^2 
  error_lmolsenP <- (test_set$yield - pred_lmolsenP)^2

  loss <- rbind(loss,cbind(error_DGT, error_olsenP, error_lmDGT, error_lmolsenP))
  loss
}
loss <- as.data.frame(loss)
names(loss) <- c("nlDGT", "nlolsenP", "lmDGT", "lmolsenP")
apply(loss,2,mean, na.rm = T)

t.test(loss$nlDGT, loss$nlolsenP, paired =T )
Z <- loss$nlDGT - loss$nlolsenP
qqnorm(Z)
qqline(Z)
plot(Z)
loss
qqnorm(loss$nlolsenP)
qqline(loss$nlolsenP)
loss$nlDGT
loss$nlolsenP
mean(loss$nlDGT) + sd(loss$nlDGT)/sqrt(36) * qt(0.975, 35)

```

```{r}
set.seed(-1825)
data_CV <- data_fos
level <- levels(data_CV$location)
N <- length(level)

s <- sample(N)
K_fold <- N


accuracy <- c()
random_index <- split(sample(c(1:N),N), c(1:K_fold))

animation::saveGIF({
  for (i in c(1:K_fold)){
    loss_ind1 = i*4-4
    loss_ind2 = i*4
  
    train_set <- subset(data_CV, location != level[i])
    test_set <- subset(data_CV, location == level[i])
    
    data_plot <- train_set %>% 
      tidyr::gather("method", "value", DGT, olsenP) %>% 
      dplyr::mutate(method = as.factor(method))
  
    levels(data_plot$method) <- c("DGT [µg/L]", "olsenP [mg/100 g]")
    
    p1 <- ggplot(data_plot %>% dplyr::filter(method == "DGT [µg/L]"), aes(x = value, y = yield)) +
      geom_point() +
      #geom_abline(data = data_plot, mapping = aes(slope = slope, intercept = intercept, col = "Linear")) +
      stat_smooth(method = 'nls', formula = 'y ~ alfa * x/(beta + x)',
                   method.args = list(start=list(alfa = 90 , beta = 1)), se=F, data = data_plot, 
                  mapping = aes(col = "Michaelis-Menten"), fullrange = T) +
      xlab("Bioavailable phosphorous") +
      ylab("Yield [hkg/ha.]") +
      theme(legend.title = element_blank()) +
      theme(legend.position = "bottom") +
      ylim(20, 90) +
      xlim(0, 160) +
      annotate(geom = "text", x = 80, y = 40, 
               label = paste0("Fold: ", i, paste0("\nMean loss: ", round(mean(loss$nlDGT[loss_ind1:loss_ind2]), digits = 2)))) +
      ggtitle("DGT [µg/L]")
    
    p2 <- ggplot(data_plot %>% dplyr::filter(method == "olsenP [mg/100 g]"), aes(x = value, y = yield)) +
      geom_point() +
      #geom_abline(data = data_plot, mapping = aes(slope = slope, intercept = intercept, col = "Linear")) +
      stat_smooth(method = 'nls', formula = 'y ~ alfa * x/(beta + x)',
                   method.args = list(start=list(alfa = 90 , beta = 1)), se=F, data = data_plot, 
                  mapping = aes(col = "Michaelis-Menten"), fullrange = T) +
      xlab("Bioavailable phosphorous") +
      ylab("Yield [hkg/ha.]") +
      theme(legend.title = element_blank()) +
      theme(legend.position = "bottom") +
      ylim(20, 90) +
      xlim(2, 9) +
      annotate(geom = "text", x = (9+2)/2, y = 40, 
               label = paste0("Fold: ", i, paste0("\nMean loss: ", round(mean(loss$nlolsenP[loss_ind1:loss_ind2]), digits = 2)))) +
      ggtitle("olsenP [mg/100 g]")
    
    p <- gridExtra::grid.arrange(p1, p2, ncol = 2, top = grid::textGrob("Fits in 9 fold CV", gp=grid::gpar(fontsize=20,font=3)))
    
    print(p)
  }
}, movie.name = "9fold_cv.gif", interval = 1)

for (i in c(1:9)){
  
  print(mean(loss$nlolsenP[i*4-4:i*4]))
}

loss$nlolsenP[8:12]

# data_plot <- data_fos %>% 
#   tidyr::gather("method", "value", DGT, olsenP) %>% 
#   dplyr::mutate(method = as.factor(method))
# 
# levels(data_plot$method) <- c("DGT [µg/L]", "olsenP [mg/100 g]")
# 
# ggplot(data_plot, aes(x = value, y = yield)) +
#   geom_point() +
#   #geom_abline(data = data_plot, mapping = aes(slope = slope, intercept = intercept, col = "Linear")) +
#   stat_smooth(method = 'nls', formula = 'y ~ alfa * x/(beta + x)',
#                method.args = list(start=list(alfa = 90 , beta = 1)), se=F, data = data_plot, mapping = aes(col = "Michaelis-Menten")) +
#   facet_wrap(~method, scales = "free") +
#   xlab("Bioavailable phosphorous") +
#   ylab("Yield [hkg/ha.]") +
#   theme(legend.title = element_blank()) +
#   theme(legend.position = "bottom")
```

```{r}
data.frame(est = c(179.5, 474.3), lwr.ci = c(147, 282), upr.ci = c(212, 693), Model = c("DGT", "olsenP")) %>% 
  ggplot(aes(Model, est)) + 
  geom_point(col = "blue") +
  ylim(0, 700) +
  geom_errorbar(aes(ymin = lwr.ci, ymax = upr.ci, width = 0.1), col = "red") +
  #annotate(geom = "text", x = 1.3, y = 179.5, label = "67 %") +
  #annotate(geom = "text", x = 2.3, y = 474.3, label = "69 %") +
  ylab("Loss") +
  theme(aspect.ratio = 1.65) +
  ggtitle("Performance of the models")

ggsave("performance.png")
```



### Bootstrapping for MSE confidence intervals
Difference in performance with Michaelis Menten fitted to DGT vs olsenP
Non parametric bootstrapping. Sampler fra forskel i loss af de to modeller. Udregner mean af disse forskelle og bestemmer konfidens intervaller.
```{r}
a <- 0.05
bootstap_DGT <- replicate(10000,mean(sample(loss$nlDGT, replace = T)))
bootstap_olsenP <- replicate(10000,mean(sample(loss$nlolsenP, replace = T)))
bootstrap_Z <- replicate(10000,mean(sample(Z, replace = T)))
CIs_MSE <- data.frame(rbind(
quantile(bootstap_DGT, c(a/2, 1-a/2)),
quantile(bootstap_olsenP, c(a/2, 1-a/2)),
quantile(bootstrap_Z, c(a/2, 1-a/2))), row.names = c("MSE_DGT","MSE_olsenP","MSE_diff"))
names(CIs_MSE) <- c("2.5%","97.5%")
CIs_MSE

p <- data.frame(loss_diff = bootstrap_Z) %>% 
  ggplot(aes(loss_diff)) + 
  geom_density(fill = "skyblue") +
  xlab("Difference in loss") 

d <- ggplot_build(p)$data[[1]]

q <- CIs_MSE["MSE_diff",] %>% tidyr::gather() %>% dplyr::pull(value)


p <- p + 
  geom_area(subset(d, x < q[1]), mapping = aes(x = x, y = y), alpha = .5, fill = "red") +
  geom_area(subset(d, x > q[2]), mapping = aes(x = x, y = y), alpha = 1, fill = "red") +
  ggtitle("Bootstraping of the difference in loss") +
  theme(plot.title = element_text(hjust = 0.5))
  

p

ggsave("bootstrap_ci.png", p)

```


### Rank Sum Test 

Difference in performance with Michaelis Menten fitted to DGT vs olsenP
Concatenates loss af DGT og olsenP. Bestemmers størrelseordenen af denne vektor og finder rank sum for DGT.
Derefter laves permutationer af vektor med 1-72 og rank sum af de 36 første bestemmes og sammenlignes med rank sum for DGT

```{r}
Z_RST <- order(c(loss$nlDGT, loss$nlolsenP))
DGT_RS <- sum(Z_RST[1:36])
olsenP_RS <- sum(Z_RST[37:72])
RST <- c()
for (i in 1:1000){
  RST_sample <- sample(length(Z_RST))
  RST <- c(RST,sum(RST_sample[1:36]))
}
p_val <- 2*mean(DGT_RS<RST)
p_val2 <- 2*mean(olsenP_RS<RST)
hist(RST)
abline(v = DGT_RS)
sum(Z_RST)
2*mean(DGT_RS>RST)
2*mean(olsenP_RS<RST)
sum(1:72)
DGT_RS <- sum(Z_RST[1:length(Z_RST)/2])
RST <- c()
for (i in 1:1000){
  RST_sample <- sample(length(Z_RST))
  RST <- c(RST,sum(RST_sample[1:length(Z_RST)/2]))
}
p_val <- 2*mean(DGT_RS>RST)

hist(RST)
abline(v = DGT_RS)
p_val

```

### LEAVE 4 OUT!!!!


```{r}
data_CV <- data_fos
level <- levels(data_CV$location)
N <- length(level)

s <- sample(N)
K_fold <- N


#accuracy <- c()
#random_index <- split(sample(c(1:N),N), c(1:K_fold))
loss <- c()

for (i in sample(c(1:K_fold))){
  print(i)

  train_set <- subset(data_CV, location != level[i])
  test_set <- subset(data_CV, location == level[i])
  model_cv_DGT <- phos.model.DGT_perm <- nls(yield ~ alfa * DGT/(beta + DGT) , data = train_set,
                        start = list(alfa = 90 , beta = 1))
  
  model_cv_olsenP <- phos.model.DGT_perm <- nls(yield ~ alfa * olsenP/(beta + olsenP) , data = train_set,
                        start = list(alfa = 90 , beta = 1))
  
  lm_model_DGT <- lm(data = data_fos, formula = yield ~ DGT)
  lm_model_olsenP <- lm(data = data_fos, formula = yield ~ olsenP)
  
  
  pred_DGT <- predict(model_cv_DGT, test_set)
  pred_olsenP <- predict(model_cv_olsenP, test_set)

  pred_lmDGT <- predict(lm_model_DGT, test_set)
  pred_lmolsenP <- predict(lm_model_olsenP, test_set)

  
  error_DGT <- (test_set$yield - pred_DGT)^2
  error_olsenP <- (test_set$yield - pred_olsenP)^2
  
  error_lmDGT <- (test_set$yield - pred_lmDGT)^2 
  error_lmolsenP <- (test_set$yield - pred_lmolsenP)^2

  loss <- rbind(loss,cbind(error_DGT, error_olsenP, error_lmDGT, error_lmolsenP))
  loss
}
loss <- as.data.frame(loss)
names(loss) <- c("nlDGT", "nlolsenP", "lmDGT", "lmolsenP")
apply(loss,2,mean)
qqnorm(Z)
t.test(loss$nlDGT, loss$nlolsenP, paired =T )
```



# Influence of phosphorous


## Permutation - med hensyn til grupper ... 

```{r}
set.seed(1997)
n <- 1000
data_permutation <- data_fos

permutation_list <- split(data_permutation$yield, data_permutation$location)

results <- c()

for (i in 1:n){
  permutation <- sample(9)
  data_permutation$yield = unlist(permutation_list[permutation])
  phos.model.DGT_perm <- nls(yield ~ alfa * DGT/(beta + DGT) , data = data_permutation,
                        start = list(alfa = 90 , beta = 1), nls.control(warnOnly = T, minFactor = 0))
  
  # phos.model.olsenP_perm <- nls(yield ~ alfa * olsenP/(beta + olsenP) , data = data_permutation,
  #                           start = list(alfa = 90 , beta = 1), nls.control(warnOnly = T))
  # 
  # lm_model_DGT_perm <- lm(data = data_permutation, formula = yield ~ DGT)
  # lm_model_olsenP_perm <- lm(data = data_permutation, formula = yield ~ olsenP)
  results <- rbind(results, c(coef(phos.model.DGT_perm)))
  
  # results <- rbind(results, c(coef(phos.model.DGT_perm), coef(phos.model.olsenP_perm), coef(lm_model_DGT_perm), coef(lm_model_olsenP_perm)))

}
results <- as.data.frame(results)
names(results) <- c("alpha", "beta")
results
# names(results) <- c("a-DGT", "b-DGT", "a-olsenP", "b-olsenP", "int. DGT", "slope DGT", "int. olsenP", "slope olsenP")

P_a_perm_DGT <- 2*mean(alfa_DGT < results$alpha)
# P_a_perm_olsenP <- 2*mean(alfa_olsenP < results$`a-olsenP`)
P_b_perm_DGT <- 2*mean(beta_DGT < results$beta)
# P_b_perm_olsenP <- 2*mean(beta_olsenP < results$`b-olsenP`)

CI_a_DGT_perm <- quantile(results$alpha, c(a/2, 1-a/2))
# CI_a_olsenP_perm <- quantile(results$`a-olsenP`, c(a/2, 1-a/2))
CI_b_DGT_perm <- quantile(results$beta, c(a/2, 1-a/2))
# CI_b_olsenP_perm <- quantile(results$`b-olsenP`, c(a/2, 1-a/2))

# par(mfrow = c(1,2))
# ggplot(data = results)
# hist(results$`a-DGT`)
# abline(v = c(CI_a_DGT_perm, alfa_DGT), col = c(2,2,1))

# hist(results$`a-olsenP`)
# abline(v = c(CI_a_olsenP_perm,alfa_olsenP), col = c(2,2,1))

# hist(results$`b-DGT`)
# abline(v = c(CI_b_DGT_perm,beta_DGT), col = c(2,2,1))

df_vlines <- data.frame("alpha" = c(CI_a_DGT_perm,alfa_DGT), "beta" = c(CI_b_DGT_perm, beta_DGT )) %>% tidyr::gather()
df_vlines

results %>% tidyr::gather() %>% 
    ggplot(aes(value)) + 
    geom_histogram(fill = 'orange', alpha = 0.7)   + 
    geom_vline(data = df_vlines, mapping = aes(xintercept = value, colour =  c('95% confidence Interval','95% confidence Interval','Observed value','95% confidence Interval','95% confidence Interval','Observed value')), show.legend = T, size = 1) +
    facet_wrap(~key, scales = 'free', labeller = label_parsed ) +
    xlab("Parameter Value") +
    ylab("Count") +
    theme(legend.title = element_blank(),
          legend.position = 'bottom')
    ggsave("PermutationTest.png")
    

# hist(results$`b-olsenP`)
# abline(v = c(CI_b_olsenP_perm,beta_olsenP), col = c(2,2,1))

p_vals_perm <- data.frame(a_DGT = c( CI_a_DGT_perm, alfa_DGT,P_a_perm_DGT), b_DGT = c( CI_b_DGT_perm, beta_DGT,P_b_perm_DGT), row.names =c("2.5 %", "97.5 % ", "observed value", "p-value"))
p_vals_perm

# p_vals_perm <- data.frame(a_DGT = c( CI_a_DGT_perm, alfa_DGT,P_a_perm_DGT), b_DGT = c( CI_b_DGT_perm, beta_DGT,P_b_perm_DGT), a_olsenP = c( CI_a_olsenP_perm,alfa_olsenP,P_a_perm_olsenP), b_olsenP = c(CI_b_olsenP_perm, beta_olsenP,P_b_perm_olsenP), row.names =c("2.5 %", "97.5 % ", "observed value", "p-value"))
# p_vals_perm
```




```{r}
data_fos
model <- lm(data = data_fos, formula = yield ~ location)
summary(model)
anova(model)
par(mfrow = c(1,2))
boxplot(data_fos$yield ~ data_fos$location)
plot(data_fos$yield ~ data_fos$location, ylim = c(0,100))
points(data_fos$yield ~ data_fos$location, col = 2)
coef(model)

```







