---
title: "Project1"
author: "Peter"
date: "1/12/2020"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#set seed
set.seed(-1825)

# load packages
library(magrittr)
library(ggplot2)
```



#DATA

## Loading data

```{r dataload}
data <- get(load("armdata.Rdata"))

```

## Rename data

```{r rename_data}
names(data) <- paste0("experiment_", 1:16)

for (expe in c(1:length(data))){
  names(data[[expe]]) <- paste0("person_", 1:10)
  for (per in c(1:length(data[[expe]]))) {
    names(data[[expe]][[per]]) <- paste0("repetion_", 1:10)
    for (rep in c(1:length(data[[expe]][[per]]))) {
      colnames(data[[expe]][[per]][[rep]]) <- c("x", "y", "z")
    }
  }
}


```

## Data long

Reads data as a "long" matrix with 7 columns - one with experiment, one with person, one with repetition, one with time and three with x, y and z.

NA's are removed by inserting the value from the next one in the row, as we are looking at trajectories and these two values therefore must be close to each other.

```{r data_long}
data_long <- as.data.frame(data)

data_long <- data_long %>%
  tidyr::gather(key = "col_name", value = "value") %>%
  tidyr::separate(col_name, c("experiment", "person", "repetition", "direction"), sep = "\\.") %>%
  dplyr::mutate(experiment = as.numeric(stringr::str_remove(string = experiment, pattern = ".*\\_"))) %>%
  dplyr::mutate(person = as.numeric(stringr::str_remove(string = person, pattern = ".*\\_"))) %>%
  dplyr::mutate(repetition = as.numeric(stringr::str_remove(string = repetition, pattern = ".*\\_"))) %>%
  dplyr::mutate(time = rep(1:100, dim(data_long)[2])) %>% 
  dplyr::mutate(experiment = as.factor(experiment), 
                person = as.factor(person), 
                repetition = as.factor(repetition),
                time = as.factor(time)) %>% 
  tidyr::spread(direction, value)

data_long[, c("x", "y", "z")] <- lapply(data_long[, c("x", "y", "z")], fromLast = T, zoo::na.locf)  #replace NA's with the next observation


cat("Head of data long")
head(data_long)
cat("Dimensions of data long: ", dim(data_long))

```

### Summary of data

```{r data_summary}
summary(data_long)
str(data_long)
```


## Data wide

Reads data as a "wide" matrix with 302 columns, one with person, one with repetition and 300 with x, y and z

```{r data_wide}
data_wide <- data_long %>%
  tidyr::gather(direction, value, x, y, z) %>% 
  dplyr::mutate(experiment = as.numeric(experiment), person = as.numeric(person), repetition = as.numeric(repetition)) %>% 
  tidyr::unite(position, direction, time, sep = "_") %>%
  tidyr::spread(position, value) %>%
  dplyr::arrange(experiment, person, repetition) %>%
  dplyr::mutate(experiment = as.factor(experiment), person = as.factor(person), repetition = as.factor(repetition))

data_wide <- data_wide[,gtools::mixedorder(colnames(data_wide))]

cat("Head of data long")
head(data_wide)
cat("Dimensions of data long: ", dim(data_wide))

```

## Data for experiment 5

```{r data_exp5}
data_exp5 <- data[["experiment_5"]]
data_long_exp5 <- data_long %>% dplyr::filter(experiment == 5)
data_wide_exp5 <- data_wide %>% dplyr::filter(experiment == 5) %>% dplyr::select(-experiment)

cat("Head of data long for experiment 5, with the dimensions: ", dim(data_long_exp5))
head(data_long_exp5)
cat("\nHead of data wide for experiment 5, with the dimensions: ", dim(data_wide_exp5))
head(data_wide_exp5)
```

## Plots of data

### One repetition

Plot of the first repetition for person 1 in experiment 5

```{r single_rep}
rgl::plot3d(data_exp5$person_1$repetion_1, type = 'p', col = heat.colors(1000), lwd = 2, xlab = 'x', ylab = 'y', zlab = 'z')
```

### Multiple repetions

All trajectories from all experiments

```{r all_trajectories}
cat("All trajectories where each color is an experiment: ")
rgl::lines3d(x = data_long$x, y = data_long$y, z = data_long$z, col = data_long$experiment)

cat("All trajectories where each color is a person: ")
rgl::lines3d(x = data_long$x, y = data_long$y, z = data_long$z, col = data_long$person)
```

Trajectories for experiment 5

```{r trajectories_exp5}
cat("Trajectories for experiment 5 where each color is a person: ")
rgl::lines3d(x = data_long_exp5$x, y = data_long_exp5$y, z = data_long_exp5$z, col = data_long_exp5$person)
```




# 1. Machine learning

## Standardization of data wide

```{r standardisation}
data_wide_exp5_norm <- data_wide_exp5
data_wide_exp5_norm[,-c(1, 2)] <- scale(data_wide_exp5[,-c(1, 2)])
```


##  PCA - test

### Method 1: SVD

```{r svd}
svd <- svd(data_wide_exp5_norm[,3:302])
PC <- as.matrix(data_wide_exp5_norm[,3:302]) %*% svd$v

# plot
ggplot(data = as.data.frame(PC), aes(x = V1, y = V2, col = data_wide_exp5$person, legend = "Person")) + 
  geom_point() +
  scale_colour_discrete(name = "Person")


cat("Head of diagonals from SVD: \n")
head(svd$d)

```

### Method 2: built in pca

```{r pca}
pca <- prcomp(x = data_wide_exp5[,-c(1,2)], scale. = T, center = T)
pca_summary <- summary(pca)

cat("Importance of the first 10 principal components")
pca_summary$importance[,1:10]

```


# Cross-Validation KNN (1 Neighbour) & Logistic Regression
*Korrekt brug af McNemar? Binomial eller med continuity correction * \
*Konfidens intervaller - Beta funktion?*

```{r determine_k}
data_CV <- data_wide_exp5

N <- nrow(data_CV)
s <- sample(N)
K_fold <- N

K <- c(1:20)

loss <- matrix(rep(NA, length(K) * K_fold), nrow = length(K))
random_index <- sample(c(1:100), 100)

 
for (i in c(1:K_fold)){
  print(paste0("Fold ", i))
  
  train_set <- data_CV[random_index[-i],]
  test_set <- data_CV[random_index[i],]
  
  for (k in K){
    pred_KNN <- class::knn(train_set[,-c(1,2)], test_set[,-c(1,2)], train_set$person, k = k)
    loss_KNN <- mean(pred_KNN != test_set$person)
    loss[k,i] <- loss_KNN
  }
}

loss <- as.data.frame(loss)

plot(apply(loss,1,mean))
```


```{r CV_models}
data_CV <- data_wide_exp5
set.seed(-1825)
N <- nrow(data_CV)
s <- sample(N)
K_fold <- N

K <- c(1:20)

accuracy <- c()
random_index <- sample(c(1:100), 100)
 
for (i in c(1:K_fold)){
  print(paste0("Fold ", i))
  f <- c(1:K_fold)[-i]
  train_set <- data_CV[random_index[-i],]
  test_set <- data_CV[random_index[i],]
  
  pred_KNN <- class::knn(train_set[,-c(1,2)], test_set[,-c(1,2)], train_set$person, k = 1)
  acc_KNN <- pred_KNN == test_set$person
  
  LogReg <- nnet::multinom(data = train_set[,-2], formula = person ~ ., MaxNWts = 10000)
  pred_LogReg <- predict(LogReg, test_set[,-c(1,2)])
  acc_LogReg <- pred_LogReg == test_set$person

  
  accuracy <- rbind(accuracy, cbind(acc_KNN, acc_LogReg))

  
}
accuracy <- as.data.frame(accuracy)
apply(accuracy,2,mean)


```



## McNemar

```{r evaluating_models}
n_11 <- sum(accuracy$acc_KNN == T & accuracy$acc_LogReg == T)
n_12 <- sum(accuracy$acc_KNN == T & accuracy$acc_LogReg == F)
n_21 <- sum(accuracy$acc_KNN == F & accuracy$acc_LogReg == T)
n_22 <- sum(accuracy$acc_KNN == F & accuracy$acc_LogReg == F)
contingency <- matrix(c(n_11, n_21, n_12, n_22),nrow = 2)

contingency

mc_nemar_result <- mcnemar.test(contingency, correct = T)
CI_KNN <- DescTools::BinomCI(sum(accuracy$acc_KNN), 100, method = "jeffrey")
CI_LogReg <- DescTools::BinomCI(sum(accuracy$acc_LogReg), 100, method = "jeffrey")

cat("Confidence interval for logistic regression")
CI_LogReg
qbeta(0.975, sum(accuracy$acc_LogReg) + 0.5, 100 - sum(accuracy$acc_LogReg)+0.5)

cat("Confidence interval for KNN")
CI_KNN

cat("Result of McNemars test")
mc_nemar_result
cat("P-value obtained via a binomial dsitribution")
2* pbinom(min(n_12,n_21) , n_12+n_21 , 1/2)
```


# 2. Statistik
Test om der er signifikant effekt af 'experiment' på de resulterende kurver.

## Mean curve 

Beregner mean-curve for hvert eksperiment.
```{r}
mean_curves <- c()
for (i in 1:16){
  for (j in 1:100){
    
    mean_point <- apply(subset(subset(data_long, experiment == i), time == j)[,c(5:7)], 2, mean)
    mean_curves <- rbind(mean_curves, c(i,j,mean_point))
    
  }
}

mean_curves <- as.data.frame(mean_curves)

cat("Plot of the mean curves")
rgl::plot3d(mean_curves$x, mean_curves$y, mean_curves$z, type = 'p', col = mean_curves$V1, lwd = 2, xlab = 'x', ylab = 'y', zlab = 'z')
  
```


### t-test between all experiments

Mange one sample t-test, hvor længden imellem hvert punkt i hvert eksperiment sammenlignes.
Nul-hypotese: den gennemsnitlige afstande imellem punkterne i to kurver er 0.
Resultatet giver en dataframe rækker svarene til sammenligning af samtlige kombinationer af de 16 eksperimenter.
Konfidens intervaller. \
*One sample t-test med afstand i mellem punkter? - Næh, det må man ikke *
*ANOVA - Forskel i mean af X, Y og Z eksperimenterne imellem*


```{r}
names(mean_curves) <- c("Experiment", "Time", "X", "Y", "Z")
combinations <- combn(1:16, 2)
n <- ncol(combinations)
dist_df <- c()
for (i in 1:n){
  curve1 <- subset(mean_curves, Experiment == combinations[1,i])[,c(3:5)]
  curve2 <- subset(mean_curves, Experiment == combinations[2,i])[,c(3:5)]
  distance <- c(combinations[1,i], combinations[2,i], sqrt(apply((curve1 - curve2)^2, 1, sum)))
  dist_df <- rbind(dist_df, distance)
}


dist_df <- as.data.frame(dist_df)

p_vals <- c()
for (i in 1:nrow(dist_df)){
  test <- t.test(dist_df[i, -c(1,2)])
  p_vals <- rbind(p_vals, c(paste0(dist_df[i,1],"-", dist_df[i,2]), test$conf.int[1], test$conf.int[2], test$p.value))
  
}


p_vals <- as.data.frame(p_vals)
names(p_vals) <- c("Experiments","Lower", "Upper", "P-value")

p_vals$`P-value` <- as.double(levels(p_vals$`P-value`))
p_vals["Adjusted P-values"] <- p.adjust(p_vals$`P-value`, method = "hochberg")

head(p_vals)
plot(sort(p_vals$`Adjusted P-values`))
```

## ANOVA

Boxplots and anova table

```{r}

par(mfrow = c(1,3))
boxplot(data_long$x ~ data_long$experiment)
boxplot(data_long$y ~ data_long$experiment)
boxplot(data_long$z ~ data_long$experiment)


model_anova <- aov(data = data_long, formula = z ~ experiment )
summary(model_anova)
summary.lm(model_anova)

head(TukeyHSD(model_anova))

```

### Min-max ANOVA

Each curve is compressed down to containing only the difference in its max and min in each direction. An ANOVA is then carried out for each direction. The p-values for each direction is adjusted by different measures of adjustment and put in a data frame.

```{r}
diff_data <- data_long %>% 
  tidyr::gather(direction, value, x, y, z) %>% 
  dplyr::group_by(experiment, person, repetition, direction) %>% 
  dplyr::summarise(diff = max(value, na.rm = T) - min(value, na.rm = T)) %>% 
  tidyr::spread(direction, diff) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(experiment = as.factor(experiment)) 
  
cat("Differences between max and mix for each rep")
head(diff_data)


lm_x <- lm(data = diff_data, x ~ experiment)
lm_y <- lm(data = diff_data, y ~ experiment)
lm_z <- lm(data = diff_data, z ~ experiment)

anova_x <- anova(lm_x)
anova_y <- anova(lm_y)
anova_z <- anova(lm_z)

p_vals_normal <- c(x = anova_x$`Pr(>F)`[1], y = anova_y$`Pr(>F)`[1], z = anova_z$`Pr(>F)`[1])
p_vals_hoch <- p.adjust(p_vals_normal, method = "hochberg")
p_vals_bonf <- p.adjust(p_vals_normal, method = "bonferroni")
p_vals_BH <- p.adjust(p_vals_normal, method = "BH") #benjamini hochberg


p_vals_anova <- data.frame(normal = p_vals_normal, hochberg = p_vals_hoch, bonferroni = p_vals_bonf, BH = p_vals_BH )

rm(p_vals_normal, p_vals_hoch, p_vals_bonf, p_vals_BH )

p_vals_anova

```

